\begin{frame}[t, fragile]{Variables don't exist in Haskell.}

Once this is all complete, the binding \mintinline[fontsize=\normalsize]{haskell}{my_var_1} is considered immutable; that is, its value cannot be changed. The Haskell
compiler will not allow destructive updates to \mintinline[fontsize=\normalsize]{haskell}{my_var_1}.

\textcolor{green}{According to ChatGPT, the first line of code after the let statement in the previous code snippet,
does not create the value itself. But what does this actually mean? Does this mean that the value \mintinline[fontsize=\normalsize]{haskell}{my_var_1}
does not get created, or does it mean that its associated value, i.e. 1, does not get created?}

To achieve the same effect of creating a binding under C++, you would need to declare \mintinline[fontsize=\normalsize]{haskell}{my_var_1} as follows;

\begin{minted}[linenos=false]{C++}
const
int my_var_1 = 1;
\end{minted}

This is probably not a perfect analogy, as I'm sure in C++ you can probably get around its ``const-ness'' by way of
pointers and/or casts if you really wanted to; but it's a general observation nonetheless.

\end{frame}


\begin{frame}[t, fragile]{Shadowing of bindings in Haskell.}

Next, consider another snippet of Haskell code;

\begin{minted}[linenos=true]{haskell}
import Text.Printf (printf)

main :: IO ()
main = do

    let

        my_var_1 :: Int
        my_var_1  = 1

    printf "my_var_1 = %d\n" my_var_1
    my_var_1 <- returnNumber2 ()
    printf "my_var_1 = %d\n" my_var_1
\end{minted}

Running this code will display;

\begin{minted}[linenos=false]{console}
my_var_1 = 1
my_var_1 = 2
\end{minted}

\end{frame}


\begin{frame}[t, fragile]{Shadowing of bindings in Haskell.}

Why is this the result, or more to the point, why did the compiler allow the code to compile in the first place? Isn't
\mintinline[fontsize=\normalsize]{haskell}{my_var_1} meant to be immutable; and if so, then what is going on here?

According to ChatGPT, the compiler is creating another binding which is also called \mintinline[fontsize=\normalsize]{haskell}{my_var_1} and which has a value
of 2. This version of \mintinline[fontsize=\normalsize]{haskell}{my_var_1} is effectively ``shadowing'' the original version which was created in the let block.
ChatGPT also says that once the later version of \mintinline[fontsize=\normalsize]{haskell}{my_var_1} is created, we can no longer access the original version of it.
\end{frame}

\begin{frame}[t, fragile]{``Declaring'' a function in Haskell.}

A Haskell function is essentially ``declared'' in a manner which is
illustrated by the following example;

\begin{minted}[linenos=false]{haskell}
addTwoNumbers :: Int -> Int -> Int
\end{minted}

However, it is worth noting that Haskell doesn't actually refer to such a statement
as a function declaration. Instead, it refers to it as a type signature,
or a function type signature.

This function type signature tells us that the function takes two values
of type \mintinline[fontsize=\normalsize]{haskell}{Int}
as arguments, and returns an \mintinline[fontsize=\normalsize]{haskell}{Int} as the result.

\end{frame}
