% New slide.

\begin{frame}[t, fragile]{Printing to the display in Haskell.}

There are a number of functions which can be used to print to the display in Haskell. Some of them are listed below;

\begin{minted}[linenos=false]{haskell}
putStrLn
print
printf
\end{minted}

\mintinline[fontsize=\normalsize]{haskell}{putStrLn} can only handle values which are of data type \mintinline[fontsize=\normalsize]{haskell}{String}. That is, you
cannot pass it other data types like \mintinline[fontsize=\normalsize]{haskell}{Int}, \mintinline[fontsize=\normalsize]{haskell}{Float}, and
\mintinline[fontsize=\normalsize]{haskell}{Double}.

It's function type signature is;

\begin{minted}[linenos=false]{haskell}
putStrLn :: String -> IO ()
\end{minted}

This means that you can't do these;

\begin{minted}[linenos=false]{haskell}
putStrLn 42       -- Argument is of type Int
putStrLn True     -- Argument is of type Bool
putStrLn [1,2,3]  -- Argument is of type list of Ints
\end{minted}

but you can do the following;

\begin{minted}[linenos=false]{haskell}
putStrLn (show 42)
putStrLn (show True)
putStrLn (show [1,2,3])
\end{minted}

\end{frame}


\begin{frame}[t, fragile]{The \mintinline[fontsize=\normalsize]{haskell}{show} function and the \mintinline[fontsize=\normalsize]{haskell}{Show} type class.}

The \mintinline[fontsize=\normalsize]{haskell}{show} function can only be invoked on an argument, if that argument's type belongs to the \mintinline[fontsize=\normalsize]{haskell}{Show} class type. From this statement and the previous code examples, we can thus infer that the types \mintinline[fontsize=\normalsize]{haskell}{Int}, \mintinline[fontsize=\normalsize]{haskell}{Bool}, and \mintinline[fontsize=\normalsize]{haskell}{[Int]} must all belong to -- or implement the behaviour of class type \mintinline[fontsize=\normalsize]{haskell}{Show}.

\end{frame}


\begin{frame}[t, fragile]{The function \mintinline{haskell}{print}.}

Next, let us consider the function \mintinline{haskell}{print}. Rather than requiring the additional step of calling the \mintinline{haskell}{show} function first, \mintinline{haskell}{print} acts directly on the argument instead. Thus, the previous code examples can be
rewritten using \mintinline{haskell}{print} as follows; 

\begin{minted}[linenos=false]{haskell}
print 42
print True
print [1,2,3]
\end{minted}

Just like the \mintinline{haskell}{show} function, \mintinline{haskell}{print} can also handle any data types that implement the \mintinline{haskell}{Show} class type.

Its function type signature is;

\begin{minted}[linenos=false]{haskell}
print :: Show a => a -> IO ()
\end{minted}

\end{frame}


\begin{frame}[t, fragile]{Generalising/templating a function in Haskell.}

If we wanted to change this function so that it is able to operate
on other numerical types of arguments such as Doubles or Floats, how could
we go about it?

The code snippet below shows us how to do this.

\begin{minted}[linenos]{haskell}
addTwoNumbers :: Num a => a -> a -> a
addTwoNumbers arg1 arg2 =

    arg1 + arg2
\end{minted}

In this version of the function, we have used a type class constraint
to achieve this generality.

\end{frame}


\begin{frame}[t, fragile]{Generalising/templating a function in Haskell.}

Under C++, a similar analogy to this function would be;

\begin{minted}[linenos]{c++}
#include <concepts>


template <typename T>
concept Numeric =
    std::integral<T> ||
    std::floating_point<T>;

template <Numeric T>
T addTwoNumbers(T arg1, T arg2)
{
    return arg1 + arg2;
}
\end{minted}

\end{frame}
