% New slide.

\begin{frame}[t, fragile]{Haskell libraries, modules, and packages.}

In Haskell, source code can be organised into modules, libraries, and packages. \\

\textbullet{} Modules

Modules are simply individual Haskell source code files; that is, files whose
filename extension is .hs. \\

\textbullet{} Libraries

Libraries are logical collections of code. \\

\textbullet{} Packages

Packages are the units of distribution. \\

\end{frame}


% New slide.

\begin{frame}[t, fragile]{A simple .cabal file for building a library.}

An example of another .cabal file is shown on the next slide. This one can be used to build;

\begin{itemize}
    \item a library
    \item a sub-library called Utils
\end{itemize}

The library can be built by using the target whose definition is labelled library. This should result in an unnamed
library being built.\\

The sub-library called Utils can be built by using the target whose definition is labelled library Utils. This should
result in a library named Utils being built.\\

\end{frame}


% New slide.

\begin{frame}[t, fragile]{A simple .cabal file for building a library.}

\begin{minted}[linenos]{ini}
-- Package description/header omitted for the sake of brevity.


library

    hs-source-dirs: src
    exposed-modules:
        Utils
    build-depends:
        base   >=4.14 && <5,
        linear >=1.23
    default-language: Haskell2010

library utils

    hs-source-dirs: src
    exposed-modules:
        Utils
    build-depends:
        base   >=4.14 && <5,
        linear >=1.23
    default-language: Haskell2010
\end{minted}

\end{frame}


% New slide.

\begin{frame}[t, fragile]{A simple .cabal file for building a library.}

Building either the library or library Utils target from this .cabal file, will result in output which should look
something like the following;

\begin{minted}[frame=single]{console}
Resolving dependencies...
Build profile: -w ghc-9.14.1 -O1
In order, the following will be built (use -v for more details):
 - quaternion-0.1.0.0 (lib:Utils) (first run)
Configuring library 'Utils' for quaternion-0.1.0.0...
Preprocessing library 'Utils' for quaternion-0.1.0.0...
Building library 'Utils' for quaternion-0.1.0.0...
[1 of 1] Compiling Utils ( \
src/Utils.hs, \
dist-newstyle/build/x86_64-linux/ghc-9.14.1/quaternion-0.1.0.0/l/Utils/build/Utils/Utils.o, \
dist-newstyle/build/x86_64-linux/ghc-9.14.1/quaternion-0.1.0.0/l/Utils/build/Utils/Utils.dyn_o
)
\end{minted}

A few things are worth noting about this output. First, note that it tells us which Haskell compiler was used to build
the target -

Note the two entries in this output

The resulting library and sub-library files should be placed into a directory which is similar to the following;

\begin{minted}[frame=single]{console}
./dist-newstyle/build/x86_64-linux/ghc-9.14.1/mylib-0.1.0.0/build/
\end{minted}

\end{frame}


% New slide.

\begin{frame}[t, fragile]{A simple .cabal file for building a library.}

1.5 cups red lentils - well rinsed or soaked \\
1 medium onion \\
Minced garlic \\
1 medium wedge pumpkin \\
5-6 medium sized carrots \\
3 medium to large potatoes \\
1 medium red capsicum \\
2-3 handfuls of fresh green beans \\
2.5 to 3 tablespoons curry powder \\
600 mL vegetable stock \\
400 mL coconut milk \\

\end{frame}

\begin{frame}[t, fragile]{A simple .cabal file for building a library.}

Cut pumpkin, potatoes, and carrots into mid sized chunks. \\
Brown off onion in Dutch oven with some olive oil. \\
Towards the end of the process, add the curry powder and the garlic. \\
Add pumpkin, carrots, and potatoes into Dutch oven
Add Vegetable stock into the Dutch oven. \\
Cook for an hour at about 160 degrees Celsius. \\
Stir vegetables around in Dutch oven. \\
Cook for another half an hour then stir in the red capsicum. \\
Cook for another 45 minutes then stir in the green beans and coconut milk. \\
Cook for another 45 minutes or until done. \\

Serve with steamed rice.

\end{frame}

11111
22222
11111
11111
11111
11111
33333
44444
33333
66666
abcdefghijkmnopqrstuvwxyz
acdefghijklnopqrstuvwxy
abcdefghijklmnpqrstuvwxyz
The quick rown fox umped over the lazy dog.
The quick bbbbb